Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-21 paper.tex
Tweak

Another advantage of Zarr is the availabilty of several 
independent implementations across different programming languages
(see Methods). Figure~\ref{fig-whole-matrix-compute-zarr-versions}
compares the CPU time required to perform the computations
of Figure~\ref{fig-whole-matrix-compute} 
for af-dist implementations using the Zarr-Python~\cite{zarrpython},
JZarr~\cite{jzarr},
and TensorStore~\citep{tensorstore} (C++ and Python) libraries.
The version using the Tensorstore C++ API is fastest, requiring 
about 20\% less time than Zarr-Python (which is used in other
benchmarks).

>>>>

Another advantage of Zarr is the availabilty of several 
independent implementations across different programming languages
(see Methods). Figure~\ref{fig-whole-matrix-compute-zarr-versions}
compares the CPU time required to perform the computations
of Figure~\ref{fig-whole-matrix-compute} 
for af-dist implementations using the Zarr-Python~\cite{zarrpython},
JZarr~\cite{jzarr},
and TensorStore~\citep{tensorstore} (C++ and Python) libraries.
The program using the Tensorstore C++ API is fastest, requiring 
about 20\% less CPU time than the version using Zarr-Python and Numba
used in our other benchmarks.
